EuPPollNet: A European database of plant-pollinator networks

### 2024-04-16 Manuscript/Ms.qmd
habitat type and bioclimatic region -results-

@@

@@

>>>>

#Check number of studies by habitat
studies_by_habitat = data %>% 
select(Study_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) %>% 
slice_max(Habitat_count, n = 3) %>% 
mutate(EuPPollNet_habitat = tolower(EuPPollNet_habitat))
#Check number of sampling sites by habitat
networks_by_habitat = data %>% 
select(Network_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) %>% 
slice_max(Habitat_count, n = 3) %>% 
mutate(EuPPollNet_habitat = tolower(EuPPollNet_habitat))
#Check number of studies by bioregion
studies_by_bioregion = data %>% 
select(Study_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) %>% 
slice_max(Bioregion_count, n = 3) %>% 
mutate(Bioregion = tolower(Bioregion))
#Check number of sampling sites by bioregion
networks_by_bioregion = data %>% 
select(Network_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) %>% 
slice_max(Bioregion_count, n = 3) %>% 
mutate(Bioregion = tolower(Bioregion))

@@

The proportion of the major pollinator orders within the database differed across habitats and bioclimatic regions (**Figure 5**). As expected, Hymenoptera was the main taxonomic order on the majority of habitats, exceeded only by Diptera on the habitat categories of riparian vegetation, moors and heathland, and alpine grasslands. Overall, the proportion of Lepidoptera and Coleoptera was low across all habitats but Coleoptera showed a notably increase in sclerophyllous vegetation and beaches, dunes and sands habitat categories. Similar patterns were observed when exploring the pollinator proportions by bioclimatic region. In this particular case, Hymenoptera was the predominant order in all bioclimatic regions with Diptera taking more importance in Alpine and Atlantic regions. Again, Lepidoptera shows low proportions across all bioclimatic regions and Coleptera seems to be only relevant in Mediterranean regions at European level. Notably, the number of studies (**Figure 5**) and sampling sites (**Figure S2**) also differs across habitats and bioclimatic regions. The habitats sampled by a higher number of studies in the database are `r studies_by_habitat$EuPPollNet_habitat[[1]]` (`r studies_by_habitat$Habitat_count[[1]]`), `r studies_by_habitat$EuPPollNet_habitat[[2]]` (`r studies_by_habitat$Habitat_count[[2]]`) and `r studies_by_habitat$EuPPollNet_habitat[[3]]` (`r studies_by_habitat$Habitat_count[[3]]`). However, the habitats that contain a higher number of sampling sites are `r networks_by_habitat$EuPPollNet_habitat[[1]]` (`r networks_by_habitat$Habitat_count[[1]]`), `r networks_by_habitat$EuPPollNet_habitat[[2]]` (`r networks_by_habitat$Habitat_count[[2]]`) and `r networks_by_habitat$EuPPollNet_habitat[[3]]` (`r networks_by_habitat$Habitat_count[[3]]`). The bioclimatic regions with a higher number of studies are `r studies_by_bioregion$Bioregion[[1]]` (`r studies_by_bioregion$Bioregion_count[[1]]`), `r studies_by_bioregion$Bioregion[[2]]` (`r studies_by_bioregion$Bioregion_count[[2]]`) and `r studies_by_bioregion$Bioregion[[3]]` (`r studies_by_bioregion$Bioregion_count[[3]]`); and the ones that contain a higher number of sampling sites are `r networks_by_bioregion$Bioregion[[1]]` (`r networks_by_bioregion$Bioregion_count[[1]]`), `r networks_by_bioregion$Bioregion[[2]]` (`r networks_by_bioregion$Bioregion_count[[2]]`) and `r networks_by_bioregion$Bioregion[[3]]` (`r networks_by_bioregion$Bioregion_count[[3]]`).

@@

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE, out.width="100%", fig.cap= "\\textbf{Figure S2}. Barplot indicating the number of sampling sites by habitat and bioclimatic region within the database.", fig.width=8, fig.height=8}

#Check number of studies by habitat
habitat = data %>% 
select(Network_id, EuPPollNet_habitat) %>% 
distinct() %>%  
group_by(EuPPollNet_habitat) %>% 
summarise(Habitat_count = n()) %>% 
mutate(Group = "Habitat") %>% 
rename(Habitat_bioregion = EuPPollNet_habitat) %>% 
rename(Count = Habitat_count)

#Check number of studies by bioregion
bioregion = data %>% 
select(Network_id, Bioregion) %>% 
distinct() %>%  
group_by(Bioregion) %>% 
summarise(Bioregion_count = n()) %>% 
mutate(Group = "Bioregion") %>% 
rename(Habitat_bioregion = Bioregion) %>% 
rename(Count = Bioregion_count)

c = bind_rows(habitat, bioregion)

ggplot(c, aes(Habitat_bioregion, Count)) +
geom_col(fill = "gray25",width = 0.9, color="black", linewidth = 0.4) +
theme_bw()+
coord_flip(expand = F) +
ggforce::facet_col(~ factor(Group, levels=c("Habitat","Bioregion")),
        space = "free", scales = "free_y") +
ylab("Sampling sites") +
xlab(NULL) +
theme(plot.margin=unit(c(0,0,0,0), "mm"),
      axis.ticks.x = element_line(color="black"),
      strip.text.x = element_text(size=12),
      strip.background = element_rect(size=0.5, linetype="solid"),
  axis.title = element_text(face = "bold", size = 12),
axis.text = element_text(size=10))
